\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{url}

\begin{document}

\begin{titlepage}
	\begin{center}
		\begin{Huge}
			\textsc{University of Dhaka}\par
		\end{Huge}
		\begin{Large}
			Department of Computer Science and Engineering\par \vspace{1cm}
			CSE-3113 : Microprocessor & Assembly Language Lab \\[12pt]	
			Lab Report 3 : familiarizing with register based assembly programming for Cortex M4 processor for arithmetic operation
		\end{Large}
	\end{center}  	
	\begin{large}
		\textbf{Submitted By:\\[12pt]}
			Name : Tanzeem Maliat\\[8pt]
			Roll No : 51\\[12pt]
		\textbf{Submitted On : \\[12pt]}
			January 31, 2023\\[20pt]
		\textbf{Submitted To :\\[12pt]}
			Dr. Upama Kabir\\[12pt]
            Dr. Mustafizur Rahman\\[12pt]
	\end{large}
\end{titlepage}

\section{Introduction}
The objectives of this lab is to understand and have familiarize with register based assembly
programming for Cortex M4 processor for arithmetic operation. In this lab we were given 5 problems & told to debug the code line by line so that the value change in register could be easily understood.

\subsection{Problem Solving Approach}
A brief description in order solve the arithmetic operation. 
\begin{itemize}
    \item In problem 1: I did the MOV three values to three registers & then conducted the ADD operations & preserved the latest resultant to r0
    \item In problem 2: I did the MOV two values to two registers & did the SUB operation & preserved the latest result to r0.
    \item In problem 3: I did the MOV three values to three registers & did the SUB operation & preserved the latest result to r0.
    \item In problem 4: I did the MOV two values to two registers & did the MUL operation & preserved the latest result to r0.
    \item In problem 5: I did the MOV three values to three registers & assigned three values as constants & then did the ADD operation.
\end{itemize}
%%%%
%%%%


\end{document}
